Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-08 Ben_Manuscripts/transport/Outline.tex
Updated documentation and outline

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \noindent We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item We equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item We cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  \noindent We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data using 1 $\mu$s simulations
  \end{itemize}

@@

  %BJC: need to word this differently since I haven't talked about CTRW yet
  \noindent We fixed the length of each simulated trajectory so that we could compare
  the total MSD between different solutes without the influence of the ageing phenomenon.
  \begin{itemize}
	\item Ageing is defined by the tendency of the average MSD to decrease
	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
	\item The maximum measured dwell time can be no longer than the total length
	of a simulated trajectory. 
	\item As measurement time or trajectory length is increased, longer dwell times
	are incorporated into the calculation, lowering the average MSD. (See supporting
	info for demonstration)
	\item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the reported values for MSD represent the average MSD for a given
	solute after a 400 ns time lag.
  \end{itemize}

@@

  \noindent We measured the distribution of dwell times and hop lengths in order to test
  the hypothesis that solutes follow a CTRW process.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
	function, cost function penalty	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
  \end{itemize}

@@

  Using four different methods, Rowley and Roux observed peaks in the radial
  distribution function for sodium coordinated with water at an O-Na distance 
  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA as
  the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols.pdf}
  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  \caption{(a) The MSD of the simple alcohols decrease as a function of the solute size, however
  methanol's MSD is considerably higher than expected based on the Stokes-Einstein equation. 
  (b) The radial distribution functions of each simple alcohol shows a maximum close
  to the highest density of monomer head groups (dashed line, normalized for easier visual
  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
  near the pore center, which may help explain its fast dynamics. (c) Despite relatively little
  difference in the total number of hydrogen bond occurences, a given alcohol's preference
  towards hydrogen bonds with the carboxylate groups increases with molecule size. (d) The average
  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
  the pore center.}\label{fig:simple_alcohols}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  % BJC: this subfigure is probably best suited for the supporting information.
  \begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
  \caption{}\label{fig:dwell_hop_PG_GCL}
  \end{subfigure}
  \caption{The number of hydrogen bond interactions between solutes and monomers increases
  as solutes gain additional hydroxyl groups. Multiple hydroxyl groups within a solute often
  hydrogen bond in different locations simultaneously. Occasionally, all four hydroxyl groups
  of Ribose (n = 4) are involved in a hydrogen bond interaction at the same time.}\label{fig:multi_hbonds}
  \end{figure}

@@

  \noindent The amides, urea and acetamide, hydrogen bond with head groups relatively 
  infrequently, but regularly coordinate with sodium ions (See Figure~\ref{fig:ketones}).
  \begin{itemize}
    \item In an average frame, acetic acid participates in more than 12 hydrogen 
    bonds with monomer head groups while urea and acetamide participate in less than 2.
    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Given their lower propensity to hydrogen bond one might expect amides to partition
  	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
    \item The peaks in their radial density are still situated between the pore center and the
    head groups, but closer to the pore center than other solutes that hydrogen bond with 
    carboxylate groups (see Figure~\ref{fig:simple_alcohol_rdf}, for example).
    \item Both solutes spend about half of their time with their carbonyl oxygen atom 
    coordinated to a sodium ion which restrains the solutes to within the pore region
    %BJC: it's possible the solutes hop from sodium to sodium quickly meaning solutes are not always immobilized.
    %BJC: could look into lifetime of association
    \item Interestingly, the nitrogen atoms do not coordinate with any sodium ions despite
    a similar negative partial charge. The hydrogen atoms may shield this interaction.
  \end{itemize}

  Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
  the head groups.
  \begin{itemize}
    \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
    \item However, acetic acid spends more time in the pore center and therefore encounters
    more sodium ions.
    \item When an acetone molecule coordinates with a sodium ion, its polarity is 
    largely neutralized and it retreats towards the head group region where it can easily
    get trapped.
    \item Acetic acid and the amides and acetic acid have alternate hydrophlic
    groups when bound to sodium ions which increases their stability in the pore.
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
  \caption{}\label{fig:SOH_GCL_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \caption{}\label{fig:sulfur_analog_rdfs}
  \end{figure}

  \noindent Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item It spends more time in the tail region than
    ethylene glycol, where transport is inherently slower, and may contribute to some
    slower MSDs.  % Can quantify as a percentage
    \item Conversely, Mercaptoethanol also exhibits some of the highest single solute MSDs 
    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    \item This may lead to larger hops in the pore region.
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region. There are nearly 40 \% more mercaptoethanol
    molecules than ethylene glycol molecules beyond 0.8 nm from the pore center. 
%    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
%    monomer head group simultaneously,
%    \item Less frequent hydrogen bonding and an affinity for the pore region may be
%    responsible for these hops.
  \end{itemize}

@@

  \noindent DMSO has a comparable if not large MSD than acetone even though it
  is a slightly larger molecule.
  \begin{itemize}
    \item The radial density of DMSO is higher than acetone close to the pore center.
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.
  	%BJC: quantify sodium coordination O group of DMSO
  \end{itemize}

@@

  The radial density of solutes near the pore center in this set is surprisingly high
  as shown in Figure~\ref{fig:nondonors_rdf}.
  \begin{itemize}
    \item Propylene carbonate and ethyl acetate are among the largest solutes
    in this study. Their size prevents them from easily entering the tail 
    region and generally gives faster transport properties since they spend
    more time in the pore region. 
    \item However, this is not a hard rule. When a solute does overcome the 
    barrier of entry beyond the head group region, it can become trapped. All
    solutes in this set show a peak $geq$ 1 nm from the pore center which is
    likely caused by solutes that get trapped in the tail region for a significant
    amount of time.
	\item The peak density of THF is considerably offset from the pore center.
	\item Observations of single THF trajectories have revealed that it does not make
	large hops while in the pore center.
	\item THF becomes nearly immobilized while associated with sodium ions (See 
	Figure~\ref{fig:thf_sodium_coordination}).
	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
	higher than THF near the head groups. The planar shape of DMF causes it to 
	become stuck between head groups. Excursions into the pore region do not
	necessarily result in large hops.
  \end{itemize}

  Carbonyl groups continue to show high degrees of association with sodium ions. 
  \begin{itemize}
    \item The number of sodium ions coordinated to the carbonyl group of 
    propylene carbonate, dimethyl formamide, ethyl acetate are consistent with 
    that shown by acetone, all between 6 and 7 per frame (See 
    figure~\ref{fig:nondonors_hbonds})
    \item The carbonyl group of the amides studied in the previous section
    associate with sodium nearly twice as frequently as compounds that don't
    contain nitrogen (see figure~\ref{fig:ketone_hbonds}).
    \item In all cases, other polar groups on carbonyl-containing compounds
    associate with sodium in negligible amounts.
  \end{itemize}

@@

  \subsection{Design Principles}

  Water content affects pore size and strongly influence the MSD of both solutes and
  water. Experiments to understand how controllable this parameter is could be useful.

  Two routes one might want to go down:
  \begin{enumerate}
    \item Only allow water to pass
    \item Selective separation of a dissolved species.
  \end{enumerate}

  Monomers that cannot hydrogen bond. % Hard to make a monomer like this

  Separate polar molecules by creating monomers with head group components designed to
  hydrogen bond.
  \begin{itemize}
  	\item Hbond donors
	\item More incentive to dwell on walls.
  \end{itemize}

  Ions with less water coordination (or more water) so that solutes can hbond with water
  and perhaps be more inclined to stay in the pore region.

@@

  We have examined the transport characteristics of a series of small polar
  molecules in our model of the H\textsubscript{II} phase formed by 
  Na-GA3C11.

  We calculated the macroscopic diffusion coefficients of each solute as 
  approximated by a CTRW model and validated our estimates using experimental
  DOSY NMR measurements.

  We have studied the influence of water content on the diffusion coefficients.

  We showed that hydrogen bonding between solutes and Na-GA3C11 monomers plays
  a major role in mechanism by which molecules traverse the nanopores.

  We can use this intuition in order to modify our monomers for a specific 
  separation.
  \begin{itemize}
	\item Increase number of h-bond sites to increase selectivity towards water 
	over polar molecules
  \end{itemize}

>>>>

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
  available online at \texttt{https://github.com/bencoscia/llcsim}.

  \noindent We ran all molecular dynamics simulations and energy minimizations using 
  GROMACS 2018.3 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We iteratively adjusted the pore radius in our systems until the right amount of water
	fit in the pores when we ran \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \noindent We equilibrated an initial solvated configuration before adding solutes.
  \begin{itemize}
	\item First, we equilibrated the initial configuration using the `wet'
	equilibration procedure described in our previous work~\cite{coscia_understanding_2019}.
	\item Then we cross-linked the equilibrated solvated configuration using the
	cross-linking procedure described in our previous work. 
  \end{itemize}

  \noindent We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data over the course of 1 $\mu$s MD simulations
  \end{itemize}

  \subsection*{Solute Parameterization}

  %BJC: might need to reword. Most of this is taken from my last paper and adapted to solutes.
  Like we have previously done for Na-GA3C11~\cite{coscia_understanding_2019}, we
  parameterized the interaction potential for the solutes using the Generalized 
  AMBER Force Field (GAFF)~\cite{wang_development_2004} with the Antechamber package
  \cite{wang_automatic_2006} provided with AmberTools16~\cite{case_ambertools16_2016}.
  We chose GAFF because it has been parameterized for use with organic molecules. We
  assigned atomic charges using the am1bccsym method of \texttt{molcharge} shipped
  with QUACPAC from Openeye Scientific Software.

@@

  %BJC: need to word this differently since I haven't talked about CTRW yet
  \noindent We fixed the length of each simulated trajectory so that we could compare
  the total MSD between different solutes without the influence of the ageing phenomenon.
  \begin{itemize}
	\item Ageing is defined by the tendency of the average slope of an MSD curve to decrease
	as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
	\item The maximum measured dwell time can be no longer than the total length
	of a simulated trajectory. 
	\item As measurement time or trajectory length is increased, longer dwell times
	are incorporated into the calculation, lowering the average MSD.
	\item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the reported values for MSD represent the average MSD for a given
	solute after a 400 ns time lag.
  \end{itemize}

@@

  \noindent We measured the distribution of dwell times and hop lengths in order to test
  the hypothesis that solutes follow a CTRW process.
  \begin{itemize}
	\item We used the \texttt{ruptures} python package in order to identify
	breakpoints, times when hops occur, in solute trajectories.\cite{truong_ruptures:_2018}
%	(See Supporting Information for more details on chosen parameters. i.e. type of cost 
%	function, cost function penalty	tolerance, number of dimensions used)
	\item The corresponding hop lengths and dwell times between break points were 
	used to construct empirical distributions.
  \end{itemize}

@@

  Using four different methods, Rowley and Roux observed peaks in the radial
  distribution function for sodium coordinated with water at an O-Na distance 
  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA~as
  the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols.pdf}
  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing butanol with highlighted O and C
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  \caption{(a) The MSD of the simple alcohols decrease as a function of the solute size, however
  methanol's MSD is considerably higher than expected based on the Stokes-Einstein equation. 
  (b) The radial distribution functions of each simple alcohol shows a maximum close
  to the highest density of monomer head groups (dashed line, normalized for easier visual
  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
  near the pore center, which may help explain its fast dynamics. (c) Despite relatively little
  difference in the total number of active hydrogen bonds per frame, a given alcohol's preference
  towards hydrogen bonds with the carboxylate groups increases with molecule size. (d) The average
  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
  the pore center.}\label{fig:simple_alcohols}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  % BJC: this subfigure is probably best suited for the supporting information.
  \begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
  \caption{}\label{fig:dwell_hop_PG_GCL}
  \end{subfigure}
  \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
  they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
  and propylene glycol are densest close to the head group region. (b)The number of 
  hydrogen bond interactions between solutes and monomers increases as solutes gain additional
  hydroxyl groups. Often, multiple hydroxyl groups within a solute often hydrogen bond in
  different locations simultaneously. Occasionally, all four hydroxyl groups
  of Ribose (n = 4) are involved in a hydrogen bond interaction at the same time.}\label{fig:multi_hbonds}
  \end{figure}

@@

  \noindent The amides, urea and acetamide, hydrogen bond with head groups relatively 
  infrequently, but regularly coordinate with sodium ions (See Figure~\ref{fig:ketones}).
  \begin{itemize}
    \item In an average frame, acetic acid participates in more than 12 hydrogen 
    bonds with monomer head groups while urea and acetamide participate in less than 2.
    \item Urea and Acetamide both have hydrogen bond donating nitrogen atoms, however
  	nitrogen is a weaker hydrogen bond donor than oxygen due to its lower electronegativity.
  	\item Given their lower propensity to hydrogen bond one might expect amides to partition
  	out of the pore and/or to move through the pore quickly, perhaps faster than methanol.
    \item The peaks in their radial density are still situated between the pore center and the
    head groups, but closer to the pore center than other solutes that hydrogen bond with 
    carboxylate groups (see Figure~\ref{fig:simple_alcohol_rdf}, for example).
    \item Both solutes spend about half of their time with their carbonyl oxygen atom 
    coordinated to a sodium ion which restrains the solutes to within the pore region
    %BJC: it's possible the solutes hop from sodium to sodium quickly meaning solutes are not always immobilized.
    %BJC: could look into lifetime of association
    \item Interestingly, only the carbonyl oxygen atoms coordinate with sodium ions. 
    The nitrogen atoms dooes not coordinate at all despite a similar negative partial
    charge. The attached hydrogen atoms may shield this interaction.
  \end{itemize}

  \noindent Acetone has the lowest MSD of this set because it is primarily trapped near and behind 
  the head groups.
  \begin{itemize}
    \item On average, acetone coordinates with sodium with the same frequency as acetic acid 
    \item However, acetic acid spends more time in the pore center and therefore encounters
    more sodium ions.
    \item When an acetone molecule coordinates with a sodium ion, its polarity is 
    largely neutralized and it retreats towards the head group region where it can easily
    get trapped.
    \item Acetic acid and the amides have other, unoccupied, hydrophilic groups while bound
    to sodium ions which increases their stability in the pore.
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_SOH.pdf}
  \caption{}\label{fig:SOH_GCL_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMP.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\linewidth}
  \includegraphics[width=\textwidth]{thiol_comparison_DMS.pdf}
  \caption{}\label{fig:DMP_GLY_comparison}
  \end{subfigure}
  \caption{(a) The RDF of mercaptoethanol is similar to ethylene glycol except 
  for its higher density in the tail region. (b) 2,3-Dimercapto-1-propanol is
  densest near the pore wall, unlike glycerol whose density is very high in the pore
  center. (c) Dimethylsulfoxide has a higher density than acetone close to the pore
  center which may in part explain its marginally larger MSD.}\label{fig:sulfur_analog_rdfs}
  \end{figure}

  \noindent Mercaptoethanol has a similar average MSD and RDF to ethylene glycol.
  \begin{itemize}
    \item There is a much larger uncertainty associated with mercaptoethanol's MSD.
    \item Some of this can be accounted for by the higher density of mercaptoethanol 
    molecules in the head group / tail region, where transport is inherently slower. 
    \item There are nearly 40 \% more mercaptoethanol molecules than ethylene 
    glycol molecules beyond 0.8 nm from the pore center. 
    \item Conversely, mercaptoethanol exhibits some of the highest single solute MSDs 
    (See Figure~\ref{fig:SOH_trace})  % Only methanol has greater (I think)
    \item It hydrogen bonds with head groups 6 times less frequently than ethylene glycol.
    \item This may lead to larger hops in the pore region.
%    \item When both hydroxyl groups of ethylene glycol are hydrogen bonded with the a
%    monomer head group simultaneously,
%    \item Less frequent hydrogen bonding and an affinity for the pore region may be
%    responsible for these hops.
  \end{itemize}

@@

  \noindent DMSO has a comparable if not larger MSD than acetone even though it
  is a slightly larger molecule.
  \begin{itemize}
    \item The radial density of DMSO is higher than acetone close to the pore center.
  	\item The pyramidal structure of DMSO may force it to spend more time closer to
  	the pore center.
  	%BJC: quantify sodium coordination O group of DMSO
  \end{itemize}

@@

  \noindent The radial density of solutes near the pore center in this set is surprisingly high
  as shown in Figure~\ref{fig:nondonors_rdf}.
  \begin{itemize}
    \item Propylene carbonate and ethyl acetate are among the largest solutes
    in this study. Their size prevents them from easily entering the tail 
    region and generally gives faster transport properties since they spend
    more time in the pore region. 
    \item However, this is not a hard rule. When a solute does overcome the 
    barrier of entry beyond the head group region, it can become trapped. All
    solutes in this set show a peak $\geq$ 1 nm from the pore center which is
    likely caused by solutes that get trapped in the tail region for a significant
    amount of time.
	\item The peak density of THF is considerably offset from the pore center.
	\item Observations of single THF trajectories have revealed that it does not make
	large hops while in the pore center.
	\item THF becomes nearly immobilized while associated with sodium ions (See 
	Figure~\ref{fig:thf_sodium_coordination}).
	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
	higher than THF near the head groups. The planar shape of DMF causes it to 
	become stuck between head groups. Excursions into the pore region do not
	necessarily result in large hops.
  \end{itemize}

  \noindent Carbonyl groups continue to show high degrees of association with sodium ions. 
  \begin{itemize}
    \item The number of sodium ions coordinated to the carbonyl group of 
    propylene carbonate, dimethyl formamide, ethyl acetate are consistent with 
    that shown by acetone, all between 6 and 7 per frame (See 
    figure~\ref{fig:nondonors_hbonds})
    \item The carbonyl group of the amides studied in the previous section
    associate with sodium nearly twice as frequently as compounds that don't
    contain nitrogen (see figure~\ref{fig:ketone_hbonds}).
    \item In all cases, other polar groups on carbonyl-containing compounds
    associate with sodium in negligible amounts.
  \end{itemize}

@@

  \subsection{Design Considerations}

  Based on our observations of the complex interactions between various polar solutes
  and the membrane's liquid crystal monomers, we can speculate on design criteria for 
  the next generation of liquid crystal monomers to be used for LLC membrane
  synthesis.
  \begin{itemize}
    \item Unfortunately, we cannot comment on the stability of the H\textsubscript{II}
    phase if major changes are made to the monomers.
    \item Therefore, our most feasible design suggestions are those which can be made
    as a post-processing step to the cross-linked membrane created using Na-GA3C11.
  \end{itemize}

  The transport properties of solutes are a strong function of the 3 trapping
  mechanisms discussed above. Therefore, it is most logical to design monomers with 
  them in mind.

  Since solutes move slowly well entangled among the monomer tails, one can try to
  design monomers that better control the partition of solutes between the pore and
  tail region.
  \begin{itemize}
    \item The head groups of Na-GA3C11 are planar which leaves a fair amount of space
    between adjacent head groups and it makes it easier for solutes to slip between and
    past them.
    \item Bulkier substituents, which do not impede stacking of monomers into columns,
    might slow the rate at which solutes partition into the tails.
    \item Additionally, one can include crosslinkable groups near the head groups in
    order to fill free volume and effectively create a wall.
    \item Finally, removal of the ether linkages between the head groups and the monomer
    tails will decrease the stability of polar molecules in the head group region.
    \item Overall, controlling the solute partition might not be the most important 
    consideration to optimize because once enough solutes flow through, the membrane tail
    region will become saturated with solute molecules and greatly reduce the rate of partition.
  \end{itemize}

  Alternatively, one can focus on designing head groups with varying hydrogen 
  bonding capabilites.
  \begin{itemize}
    \item Na-GA3C11 has a carboxylate group which readily accepts hydrogen bonds
    \item One can increase the number of hydrogen bonding sites on the head groups
    in order to trap more solutes, or decrease the number of hydrogen bond sites
    to trap less.
  \end{itemize}

  Finally, one can attempt to control the degree to which solutes coordinate 
  with counterions.
  \begin{itemize}
    \item We have observed a significant amount of sodium association with 
    negatively charge solute constituents.
    \item Changing the size and valence of the counter ion may offer some
    interesting behavior. 
    \item For example, a counter ion with a charge of +2 may attract more solute
    molecules and bind them more tightly, but there will only be half as many
    counterions in the system which may reduce its overall influence.
    \item Additionally, the size of the counterion will affect the mobility
    of any complex formed. 
    \item Sodium appears to do a good job of immobilizing complexes formed between
    it and solutes. 
    \item However, a Lithium ion might be more prone to go along for the ride.
    \item Hydrogen would likely spend the majority of its time bound to the 
    carboxylate head group or as part of a hydronium ion hence interfering with 
    solute transport infrequently.
  \end{itemize}

%  There are two types of separations for which this membrane may have some use.
%  \begin{enumerate}
%    \item In a purification process, one may only desire water to pass. In this 
%    case, water should have much faster dynamics than any other dissolved species.~\label{sep:purification}
%    \item For a separate application, one may desire to selectively separate a 
%    dissolved species from a complex stream.~\label{sep:selective}
%  \end{enumerate}

  The MSD of solutes may be much larger in more concentrated solutions because there
  will be less available trapping sites for them to occupy.
  \begin{itemize}
    \item We purposely studied the behavior of the solutes in dilute conditions.
    \item The difference in size between water and the fastest solute, methanol, is not
    enough to explain the order of magnitude difference in their average MSDs.
    \item The sheer number of water molecules prevents the majority of them from 
    becoming trapped for long periods of time.
    \item A similar effect may increase solute MSDs in more concentrated solutions.
  \end{itemize}

  As a final consideration, water content affects pore size and strongly influences
  the MSDs of solutes, water and counterions.
  \begin{itemize}
    \item The MSD of these components is about 2 orders of magnitude larger in the 
    10 wt \% system than the 5 wt \% system.
    \item The 5 wt \% system is much less feasible as a separations membrane on the basis
    of water permeability alone.
    \item Typically, the total water content used to create the H\textsubscript{II} phase
    is reported, but the amount of water that resides in the pores, tails and in between
    hexagonal mesophases is less clear.
    \item Experiments, such as those by Jenkins et al.~\cite{jenkins_identification_2012}, 
    may help elucidate the water composition in each region.
    \item The results would be extremely useful for determining the viability of a given
    LLC membrane system. 
  \end{itemize}

@@

  We have examined the transport characteristics of a series of small polar
  molecules in our model of the H\textsubscript{II} phase formed by the liquid 
  crystal monomer Na-GA3C11.

  We learned that the MSD of solutes, water and counter ions are highly dependent 
  on LLC membrane water content.
  \begin{itemize}
    \item As more water is added to the system, the pores become less crowded
    with monomer components and the MSD of water, sodium and solutes increase.
    \item The amount of water in the pores deserves special attention when 
    screening new monomers.
  \end{itemize}

  We learned that solutes undergo anomalous diffusion which can be described 
  as a subordinated fractional brownian motion process. 
  \begin{itemize}
    \item In general, solutes hop intermittently between periods of entrapment
    \item These hops are anti-correlated to their previous hops
  \end{itemize}

  We observed three mechanisms of solute entrapment.
  \begin{itemize}
    \item A solute can become stuck in the tail region. 
    \item A solute can hydrogen bond with monomers
    \item A solute can associate with a bound counterion
  \end{itemize}

  Based on these trapping mechanisms, we have suggested modifications that
  can be made to monomers in order to mitigate or enhance their effect on
  solute MSDs.
